Cross-Validation Default

### 2023-06-29 minos/validation/cross_validation_default.Rmd
Stopped saving some plots in the cross_validation_default.Rmd notebook

require(tidyverse)
require(ggplot2)
require(here)
require(scales)

@@

plot_mean_comparison(pivoted.df = nut.pivoted, 
                     var = 'nutrition_quality', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')

@@

plot_mean_comparison(pivoted.df = tobacco.pivoted, 
                     var = 'ncigs', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')

>>>>

require(tidyverse)
require(ggplot2)
require(ggExtra)
require(here)
require(scales)

@@

plot_mean_comparison(pivoted.df = nut.pivoted, 
                     var = 'nutrition_quality', 
                     group.var = 'scenario',
                     save = FALSE)

@@

plot_mean_comparison(pivoted.df = tobacco.pivoted, 
                     var = 'ncigs', 
                     group.var = 'scenario',
                     save = FALSE)
